### 2021-03-04 ch/4-structure.tex
Fix all kinds of small problems

\section{Using an unlabelled deployment set to overcome sampling bias}\label{sec:zsf}
A shortcoming of the approach from the previous chapter
is its reliance on a representative set which has \(s\) labels.
As discussed, it is necessary to make use of \emph{some} kind of side information,
but perhaps we can relax some requirements.
In particular, while it is already easier to collect data without \(y\) labels (but with \(s\) labels),
it is \emph{even} easier to collect data without \emph{any} label.
Thus, requiring only an unlabelled context set would improve the applicability of the method.
This chapter presents an approach based on that idea.

>>>>

\section{Using an unlabelled deployment set to overcome sam\-p\-ling bias}\label{sec:zsf}
A shortcoming of the approach from the previous chapter
is its reliance on a representative set which has \(s\) labels.
As discussed, it is necessary to make use of \emph{some} kind of side information,
but perhaps we can relax some requirements.
In particular, while it is already easier to collect data without \(y\) labels (but with \(s\) labels),
it is \emph{even} easier to collect data without \emph{any} label.
Thus, requiring only an unlabelled context set would improve the applicability of the method.
This chapter presents an approach based on that idea.

### 2021-03-04 paper1/paper1.tex
Fix all kinds of small problems

The method presented in this paper is closely related to a number of previous works,
e.g.\ \citet{kamiran2012data,calders2010three}.
Proper comparison with them requires knowledge of our approach.
We will thus explain our approach in the subsequent sections, and defer detailed comparisons to Section~\ref{sec:relatedwork} (Related Work).

@@

\begin{theorem}\label{th:prob}
  The probability that $y$ and $\bar{y}$ disagree ($y\neq\bar{y}$) for any input $x$ in the dataset is given by:
  \begin{align}
    P(y\neq\bar{y}|s)=P\left(\left|\eta(x,s) - \tfrac{1}{2}\right| < t_s\right)
  \end{align}
  where
  \begin{align}
    t_s = \left|\frac{m_s+2b_s-1}{2m_s}\right|~.\label{eq:def-ts}
  \end{align}
\end{theorem}
Thus, if the threshold $t_s$ is small,
then only if there are inputs very close to the decision boundary ($\eta_s(x)$ close to $\tfrac{1}{2}$)
would we have $\bar{y}\neq y$.
$t_s$ determines the accuracy penalty that we have to accept in order to gain fairness.
The value of $t_s$ can be taken into account when choosing $m_s$ and $b_s$ (see Section~\ref{sec:fairness}).
If $\eta_s$ satisfies the Tsybakov condition~\citep{tsybakov2004optimal},
then we can give an upper bound for the probability.
\begin{definition}
  A distribution $\eta$ satisfies the Tsybakov condition if there exist $C>0$, $\lambda > 0$ and $t_0\in (0,\tfrac{1}{2}]$
  such that for all $t\leq t_0$,
  \begin{align}
    P\left(\left|\eta(x)-\tfrac{1}{2}\right|<t\right)\leq Ct^\lambda~.
  \end{align}
\end{definition}
This condition bounds the region close to the decision boundary.
It is a property of the dataset.
\begin{corollary}\label{th:upperbound}
  If $\eta(x,s)=P(y=1|x,s)$ satisfies the Tsybakov condition in $x$, with constants $C$ and $\lambda$,
  then the probability that $y$ and $\bar{y}$ disagree ($y\neq\bar{y}$) for any input $x$ in the dataset is bounded by:
  \begin{align}
    P(y\neq\bar{y}|s)<C\left|\frac{m_s+2b_s-1}{2m_s}\right|^\lambda~.
  \end{align}
\end{corollary}
Section~\ref{sec:fairness} discusses how to choose the parameters for $\bar{\eta}$ in order to make it balanced.

@@

\subsection{Concrete algorithm}
For training, we are only given the unbalanced distribution $\eta_s(x)$
and not the target distribution $\bar{\eta}_s(x)$.
However, $\bar{\eta}_s(x)$ is needed in order to train a fair classifier.
One approach is to explicitly change the labels $y$ in the dataset, in order to construct $\bar{\eta}_s(x)$.
We discuss this approach and its drawback in the related work section (Section~\ref{sec:relatedwork}).
%(taken by~\citet{kamiran2012data})

@@

Corollary~\ref{col:fairacc} implies that
in the common case where group $s=0$ is disadvantaged ($r_a^0 < r_a^1$) and also underrepresented ($p<\tfrac{1}{2}$),
the highest accuracy under demographic parity can be achieved at $\mathit{PR}_t=r_a^1$ with
\begin{align}
  \mathit{acc} \leq 1 - p\cdot\left( r^1_a -r^0_a \right)~.
\end{align}
However, this means willingly accepting a lower accuracy in the (smaller) subset $\mathcal{S}_0$
that is compensated by a very good accuracy in the (larger) subset $\mathcal{S}_1$.
A decidedly ``fairer'' approach is to aim for the same accuracy in both subsets.
This is achieved by using the average of the base acceptance rates for the target rate.
As we balance the test set in our experiments, this kind of sacrificing of one demographic group does not work there.
We compare the two choices ($\mathit{PR}_t^{max}$ and $\mathit{PR}_t^{avg}$) in Section~\ref{sec:experiments}.

@@

In Fig.~\ref{fig:tar}, we investigate which choice of target ($\mathit{PR}_t^{avg}$, $\mathit{PR}_t^{min}$ or $\mathit{PR}_t^{max}$)
gives the best result.
We use $\mathit{PR}_t^{avg}$ for all following experiments as this is the fairest choice (cf. Section~\ref{sec:dp}).
The Fig.\ref{fig:tar}(a) shows results from Adult dataset with \emph{race} as sensitive attribute
where we have $\mathit{PR}_t^{min}=0.156$, $\mathit{PR}_t^{max}=0.267$ and $\mathit{PR}_t^{avg} =0.211$.
$\mathit{PR}_t^{avg}$ performs best in term of the trade-off.%equal (for \emph{race} as sensitive attribute)
%or better (for \emph{gender}) compared with the two other possibilities.
% The variant that uses $s$ for training and prediction (``use $s$'') performs significantly better here.
%\emph{ZafarAccuracy} can achieve good fairness results at the cost of accuracy.
\begin{figure}[t]
  \centering
  \includegraphics[width=0.98\textwidth]{./figures/adult_parity_scatter_pr_pr.eps}
  \caption{
    Predictions with different target acceptance rates (demographic parity) for 10 repeats.
    (a): $\mathit{PR}_{s=0}$ vs $\mathit{PR}_{s=1}$ using race as the sensitive attribute;
    (b): $\mathit{PR}_{s=0}$ vs $\mathit{PR}_{s=1}$ using gender.
  }%
  \label{fig:adult_parity_scatter_pr_pr}
\end{figure}%
\begin{figure}[t]
  \centering
  \includegraphics[width=0.98\textwidth]{./figures/adult_parity_scatter_acc.eps}
  \caption{
    Predictions with different target acceptance rates (demographic parity) for 10 repeats.
    (a): disparate impact vs accuracy on Adult dataset using race as the sensitive attribute;
    (b): disparate impact vs accuracy using gender.
  }%
  \label{fig:adult_parity_scatter_acc}
\end{figure}%

@@

Fig.~\ref{fig:adult_parity_scatter_acc}(a) and (b) show the same data
as Fig.~\ref{fig:adult_parity_scatter_pr_pr} but with different axes.
It can be seen from this Fig.~\ref{fig:adult_parity_scatter_acc}(a) and (b)
that the fairness-accuracy trade-off is usually best
when the target rate is close to the average of the positive rates in the dataset
(which is around 0.2 for both sensitive attribute).
%that the target acceptance rate can be used to \emph{control} the trade-off between accuracy and fairness.
%the target acceptance rate is not a trade-off parameter between accuracy and fairness.
%In this specific case, changing the target rate barely affects fairness and
%it only affects the accuracy because target acceptance rates that are different from the base acceptance rate
%necessarily lead to ``miss-classifications''.
% More details are given in the Appendix (Table~\ref{tab:adult-parity} and Table~\ref{tab:adult-tar}).

\subsection{Results for Equality of Opportunity on ProPublica dataset.}\label{sssec:eqoppresults}
%
For equality of opportunity,
we again follow \citet{zafar2017fairnesstreatment} and evaluate the algorithm on the ProPublica dataset.
As we did for demographic parity,
we define a measure of equality of opportunity via the ratio of the true positive rates (TPRs) within the demographic groups.
We use $\mathit{TPR}_{s=i}$ to denote the observed TPR in group $i$: $P(\hat{y}=1|y=1, s=i)$,
and $\mathit{TNR}_{s=i}$ for the observed true negative rate (TNR) in the same manner.
The measure is then given by $\mathit{TPR}_{s=0} / \mathit{TPR}_{s=1}$.
A perfectly fair algorithm would achieve $1.0$ on the measure.%
\begin{figure*}[t]
  \centering
  \includegraphics[width=0.98\textwidth]{./figures/propublica_opp_box_with_agarwal.eps}
%   \includegraphics[width=0.45\textwidth]{propublica-recidivism_race_opp_box.eps}
%   \includegraphics[width=0.45\textwidth]{propublica-recidivism_sex_opp_box.eps}
  \caption{Accuracy and fairness (with respect to \emph{equality of opportunity}) for various methods on ProPublica dataset.
    (a): using race as the sensitive attribute; (b): using gender.
    A completely fair model would achieve a value of 1.0 in the x-axis.
    %The best value for the TPR ratio is $1.0$.
    See Fig.~\ref{fig:propublica_opp_scatter_tpr}(a) and (b) on how these choices of PR setting translate to
    $\mathit{TPR}_{s=0}$ vs $\mathit{TPR}_{s=1}$. %and TPR vs TNR.
  }%
  \label{fig:propublica_opp_box}
\end{figure*}%
\begin{figure*}[!ht]
  \centering
  \includegraphics[width=0.98\textwidth]{./figures/propublica_opp_scatter_tpr.eps}
  \caption{%
    Fairness measure $\mathit{TPR}_{s=0}$ vs $\mathit{TPR}_{s=1}$ (\emph{equality of opportunity}) for different target PRs ($\mathit{PR}_t$).
    (a): on dataset ProPublica recidivism using race as the sensitive attribute;
    (b): using gender.
  }%
  \label{fig:propublica_opp_scatter_tpr}
\end{figure*}%

The results of 10 runs are shown in Fig.~\ref{fig:propublica_opp_box} and Fig.~\ref{fig:propublica_opp_scatter_tpr}.
Fig.~\ref{fig:propublica_opp_box}(a) and (b) show the accuracy-fairness trade-off;
Fig.~\ref{fig:propublica_opp_scatter_tpr}(a) and (b) show the achieved TPRs.
In the accuracy-fairness plot, varying $\mathit{PR}_t$ is shown to produce an inverted U-shape:
Higher $\mathit{PR}_t$ still leads to improved fairness, but at a high cost in terms of accuracy.

>>>>

The method presented in this paper is closely related to a number of previous works,
e.g.\ \citet{kamiran2012data,calders2010three}.
Proper comparison with them requires knowledge of our approach.
We will thus explain our approach in the subsequent sections, and defer detailed comparisons to section~\ref{sec:relatedwork} (Related Work).

@@

\begin{theorem}\label{th:prob}
  The probability that $y$ and $\bar{y}$ disagree ($y\neq\bar{y}$) for any input $x$ in the dataset is given by:
  \begin{align}
    P(y\neq\bar{y}|s)=P\left(\left|\eta(x,s) - \tfrac{1}{2}\right| < t_s\right)
  \end{align}
  where
  \begin{align}
    t_s = \left|\frac{m_s+2b_s-1}{2m_s}\right|~.\label{eq:def-ts}
  \end{align}
\end{theorem}
Thus, if the threshold $t_s$ is small,
then only if there are inputs very close to the decision boundary ($\eta_s(x)$ close to $\tfrac{1}{2}$)
would we have $\bar{y}\neq y$.
$t_s$ determines the accuracy penalty that we have to accept in order to gain fairness.
The value of $t_s$ can be taken into account when choosing $m_s$ and $b_s$ (see section~\ref{sec:fairness}).
If $\eta_s$ satisfies the Tsybakov condition~\citep{tsybakov2004optimal},
then we can give an upper bound for the probability.
\begin{definition}
  A distribution $\eta$ satisfies the Tsybakov condition if there exist $C>0$, $\lambda > 0$ and $t_0\in (0,\tfrac{1}{2}]$
  such that for all $t\leq t_0$,
  \begin{align}
    P\left(\left|\eta(x)-\tfrac{1}{2}\right|<t\right)\leq Ct^\lambda~.
  \end{align}
\end{definition}
This condition bounds the region close to the decision boundary.
It is a property of the dataset.
\begin{corollary}\label{th:upperbound}
  If $\eta(x,s)=P(y=1|x,s)$ satisfies the Tsybakov condition in $x$, with constants $C$ and $\lambda$,
  then the probability that $y$ and $\bar{y}$ disagree ($y\neq\bar{y}$) for any input $x$ in the dataset is bounded by:
  \begin{align}
    P(y\neq\bar{y}|s)<C\left|\frac{m_s+2b_s-1}{2m_s}\right|^\lambda~.
  \end{align}
\end{corollary}
Section~\ref{sec:fairness} discusses how to choose the parameters for $\bar{\eta}$ in order to make it balanced.

@@

\subsection{Concrete algorithm}
For training, we are only given the unbalanced distribution $\eta_s(x)$
and not the target distribution $\bar{\eta}_s(x)$.
However, $\bar{\eta}_s(x)$ is needed in order to train a fair classifier.
One approach is to explicitly change the labels $y$ in the dataset, in order to construct $\bar{\eta}_s(x)$.
We discuss this approach and its drawback in the related work section (section~\ref{sec:relatedwork}).
%(taken by~\citet{kamiran2012data})

@@

Corollary~\ref{col:fairacc} implies that
in the common case where group $s=0$ is disadvantaged ($r_a^0 < r_a^1$) and also underrepresented ($p<\tfrac{1}{2}$),
the highest accuracy under demographic parity can be achieved at $\mathit{PR}_t=r_a^1$ with
\begin{align}
  \mathit{acc} \leq 1 - p\cdot\left( r^1_a -r^0_a \right)~.
\end{align}
However, this means willingly accepting a lower accuracy in the (smaller) subset $\mathcal{S}_0$
that is compensated by a very good accuracy in the (larger) subset $\mathcal{S}_1$.
A decidedly ``fairer'' approach is to aim for the same accuracy in both subsets.
This is achieved by using the average of the base acceptance rates for the target rate.
As we balance the test set in our experiments, this kind of sacrificing of one demographic group does not work there.
We compare the two choices ($\mathit{PR}_t^{max}$ and $\mathit{PR}_t^{avg}$) in section~\ref{sec:experiments}.

@@

In fig.~\ref{fig:tar}, we investigate which choice of target ($\mathit{PR}_t^{avg}$, $\mathit{PR}_t^{min}$ or $\mathit{PR}_t^{max}$)
gives the best result.
We use $\mathit{PR}_t^{avg}$ for all following experiments as this is the fairest choice (cf. section~\ref{sec:dp}).
The fig.~\ref{fig:tar}(a) shows results from Adult dataset with \emph{race} as sensitive attribute
where we have $\mathit{PR}_t^{min}=0.156$, $\mathit{PR}_t^{max}=0.267$ and $\mathit{PR}_t^{avg} =0.211$.
$\mathit{PR}_t^{avg}$ performs best in term of the trade-off.%equal (for \emph{race} as sensitive attribute)
%or better (for \emph{gender}) compared with the two other possibilities.
% The variant that uses $s$ for training and prediction (``use $s$'') performs significantly better here.
%\emph{ZafarAccuracy} can achieve good fairness results at the cost of accuracy.
\begin{figure}[t]
  \centering
  \includegraphics[width=0.98\textwidth]{./figures/adult_parity_scatter_pr_pr.eps}
  \caption{
    Predictions with different target acceptance rates (demographic parity) for 10 repeats.
    (a): $\mathit{PR}_{s=0}$ vs $\mathit{PR}_{s=1}$ using race as the sensitive attribute;
    (b): $\mathit{PR}_{s=0}$ vs $\mathit{PR}_{s=1}$ using gender.
  }%
  \label{fig:adult_parity_scatter_pr_pr}
\end{figure}%
\begin{figure}[t]
  \centering
  \includegraphics[width=0.98\textwidth]{./figures/adult_parity_scatter_acc.eps}
  \caption{
    Predictions with different target acceptance rates (demographic parity) for 10 repeats.
    (a): disparate impact vs accuracy on Adult dataset using race as the sensitive attribute;
    (b): disparate impact vs accuracy using gender.
  }%
  \label{fig:adult_parity_scatter_acc}
\end{figure}%

@@

Fig.~\ref{fig:adult_parity_scatter_acc}(a) and (b) show the same data
as fig.~\ref{fig:adult_parity_scatter_pr_pr} but with different axes.
It can be seen from this fig.~\ref{fig:adult_parity_scatter_acc}(a) and (b)
that the fairness-accuracy trade-off is usually best
when the target rate is close to the average of the positive rates in the dataset
(which is around 0.2 for both sensitive attribute).
%that the target acceptance rate can be used to \emph{control} the trade-off between accuracy and fairness.
%the target acceptance rate is not a trade-off parameter between accuracy and fairness.
%In this specific case, changing the target rate barely affects fairness and
%it only affects the accuracy because target acceptance rates that are different from the base acceptance rate
%necessarily lead to ``miss-classifications''.
% More details are given in the Appendix (Table~\ref{tab:adult-parity} and Table~\ref{tab:adult-tar}).

\subsection{Results for Equality of Opportunity on ProPublica dataset.}\label{sssec:eqoppresults}
%
For equality of opportunity,
we again follow \citet{zafar2017fairnesstreatment} and evaluate the algorithm on the ProPublica dataset.
As we did for demographic parity,
we define a measure of equality of opportunity via the ratio of the true positive rates (TPRs) within the demographic groups.
We use $\mathit{TPR}_{s=i}$ to denote the observed TPR in group $i$: $P(\hat{y}=1|y=1, s=i)$,
and $\mathit{TNR}_{s=i}$ for the observed true negative rate (TNR) in the same manner.
The measure is then given by $\mathit{TPR}_{s=0} / \mathit{TPR}_{s=1}$.
A perfectly fair algorithm would achieve $1.0$ on the measure.%
\begin{figure*}[t]
  \centering
  \includegraphics[width=0.98\textwidth]{./figures/propublica_opp_box_with_agarwal.eps}
%   \includegraphics[width=0.45\textwidth]{propublica-recidivism_race_opp_box.eps}
%   \includegraphics[width=0.45\textwidth]{propublica-recidivism_sex_opp_box.eps}
  \caption{Accuracy and fairness (with respect to \emph{equality of opportunity}) for various methods on ProPublica dataset.
    (a): using race as the sensitive attribute; (b): using gender.
    A completely fair model would achieve a value of 1.0 in the x-axis.
    %The best value for the TPR ratio is $1.0$.
    See fig.~\ref{fig:propublica_opp_scatter_tpr}(a) and (b) on how these choices of PR setting translate to
    $\mathit{TPR}_{s=0}$ vs $\mathit{TPR}_{s=1}$. %and TPR vs TNR.
  }%
  \label{fig:propublica_opp_box}
\end{figure*}%
\begin{figure*}[!ht]
  \centering
  \includegraphics[width=0.98\textwidth]{./figures/propublica_opp_scatter_tpr.eps}
  \caption{%
    Fairness measure $\mathit{TPR}_{s=0}$ vs $\mathit{TPR}_{s=1}$ (\emph{equality of opportunity}) for different target PRs ($\mathit{PR}_t$).
    (a): on dataset ProPublica recidivism using race as the sensitive attribute;
    (b): using gender.
  }%
  \label{fig:propublica_opp_scatter_tpr}
\end{figure*}%

The results of 10 runs are shown in fig.~\ref{fig:propublica_opp_box} and fig.~\ref{fig:propublica_opp_scatter_tpr}.
Fig.~\ref{fig:propublica_opp_box}(a) and (b) show the accuracy-fairness trade-off;
fig.~\ref{fig:propublica_opp_scatter_tpr}(a) and (b) show the achieved TPRs.
In the accuracy-fairness plot, varying $\mathit{PR}_t$ is shown to produce an inverted U-shape:
Higher $\mathit{PR}_t$ still leads to improved fairness, but at a high cost in terms of accuracy.

### 2021-03-04 paper2/4-experiments.tex
Fix all kinds of small problems

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.7\textwidth]{./Figures/nosinn_celeba_multiplot_all_landscape_Smiling.pdf}
    \caption{
        Performance of our model for the target ``smiling'' for different mixing factors $\eta$.
        \emph{DP diff} measures fairness with respect to demographic parity.
        A perfectly fair model has a \emph{DP diff} of 0, thus the closer to top-left the better it is in terms of we accuracy-fairness trade-off.
        Only values $\eta=0$ and $\eta=1$ correspond to the scenario of a strongly biased training set.
        The results for $0.1\leq \eta\leq 0.9$ are to confirm that our model does not harm performance for non-biased training sets.
    }%
    \label{fig:celeba-multiplot}
\end{figure}

@@

Inspection of the null-samples shows that both the cVAE and cFlow model succeed in removing almost all colour information, which is supported quantitatively by Fig.~\ref{fig:cmnist_chart}.
While the cVAE outperforms cFlow marginally at low $\sigma$ values, performance degrades
%rapidly
as this increases.
This highlights the problems with the conditional decoder we anticipated in Section~\ref{conddec}.
The lower $\sigma$, and therefore the variation in sampled colour, is, the more reliably the $s$ label, corresponding to the mean of RGB distribution, encodes information about the colour.
For higher $\sigma$ values, the sampled colours can deviate far from the mean and so the encoder must incorporate information about $s$ into its representation if it is to minimise the reconstruction loss.
cFlow, on the other hand, is consistent across $\sigma$ values.

\paragraph{CelebA.}
To evaluate the effectiveness of our framework on real-world image data we use the CelebA dataset~\citep{liu2015faceattributes}, consisting of 202,599 celebrity images.
These images are annotated with various binary physical  attributes, including ``gender'', ``hair color'', ``young'', etc, from which we  select our sensitive and target attributes.
The images are centre cropped and resized to $64\times64$, as is standard practice.
For our experiments, we designate ``gender'' as the sensitive attribute,
and ``smiling'' and ``high cheekbones'' as target attributes.
We chose gender as the sensitive attribute as it a common sensitive attribute in the fairness literature.
For the target attributes, we chose attributes that are harder to learn than gender and which do not correlate too strongly with gender in the dataset
(``wearing lipstick'' for example being an attribute too closely correlated with gender).
% The sampling and evaluation procedure is identical to that conducted for the UCI Adult dataset.
% We evaluate the performance of all models for mixing factors ($\eta$) of value $\{0, 0.1, ..., 1\}$. 
The model is trained on the representative set (normal subset of CelebA)
and is then used to encode the artificially biased training set and the test set.
The results for the most strongly biased training set ($\eta=0$) can be found in Fig.~\ref{fig:celeba-targets}.
Our method outperforms the baselines in accuracy and fairness.

We also assess performance for different mixing factors ($\eta$) which correspond to varying degrees of bias in the training set
(see Fig.~\ref{fig:celeba-multiplot}).
This is to verify that the model does not \emph{harm} performance when there is not much bias in the training set.
For these experiments, the model is trained once on the representative set and is then used to encode different training sets.
The results show that for the intermediate values of $\eta$, our model incurs a small penalty in terms of accuracy,
but at the same time makes the results \emph{fairer} (corresponding to an accuracy-fairness trade-off). Qualitative results can be found in Fig.~\ref{fig:celeba_cflow} (images from cVAE can be found in section~\ref{sec:qual-results-celeba}).

@@

\paragraph{Results for the UCI Adult dataset.}
The UCI Adult dataset consists of census data and is commonly used to evaluate models focused on algorithmic fairness.
Following convention, we designate ``gender'' as the sensitive attribute $s$ and whether an individual's salary is \$50,000 or greater as $y$.
We show the performance of our approach in comparison to baseline approaches in Fig. \ref{fig:adult-chart}.
We evaluate the performance of all models for mixing factors ($\eta$) $0$ and $1$. 
Results shown in Fig. \ref{fig:adult-chart} show that
%while our model fails to surpass the baseline models in terms of accuracy for the balanced case (and those close to it),
we match or exceed the baseline.
%as $\eta$ moves the dataset towards a more imbalanced setting.
In terms of fairness metrics, our approach generally outperforms the baseline models for both of $\eta$.
Detailed results can be found in the Appendix~\ref{sec:additional-results}.

>>>>

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.85\textwidth]{./Figures/nosinn_celeba_multiplot_all_landscape_Smiling.pdf}
    \caption{
        Performance of our model for the target ``smiling'' for different mixing factors $\eta$.
        \emph{DP diff} measures fairness with respect to demographic parity.
        A perfectly fair model has a \emph{DP diff} of 0, thus the closer to top-left the better it is in terms of we accuracy-fairness trade-off.
        Only values $\eta=0$ and $\eta=1$ correspond to the scenario of a strongly biased training set.
        The results for $0.1\leq \eta\leq 0.9$ are to confirm that our model does not harm performance for non-biased training sets.
    }%
    \label{fig:celeba-multiplot}
\end{figure}

@@

Inspection of the null-samples shows that both the cVAE and cFlow model succeed in removing almost all colour information, which is supported quantitatively by fig.~\ref{fig:cmnist_chart}.
While the cVAE outperforms cFlow marginally at low $\sigma$ values, performance degrades
%rapidly
as this increases.
This highlights the problems with the conditional decoder we anticipated in section~\ref{conddec}.
The lower $\sigma$, and therefore the variation in sampled colour, is, the more reliably the $s$ label, corresponding to the mean of RGB distribution, encodes information about the colour.
For higher $\sigma$ values, the sampled colours can deviate far from the mean and so the encoder must incorporate information about $s$ into its representation if it is to minimise the reconstruction loss.
cFlow, on the other hand, is consistent across $\sigma$ values.

\paragraph{CelebA.}
To evaluate the effectiveness of our framework on real-world image data we use the CelebA dataset~\citep{liu2015faceattributes}, consisting of 202,599 celebrity images.
These images are annotated with various binary physical  attributes, including ``gender'', ``hair color'', ``young'', etc, from which we  select our sensitive and target attributes.
The images are centre cropped and resized to $64\times64$, as is standard practice.
For our experiments, we designate ``gender'' as the sensitive attribute,
and ``smiling'' and ``high cheekbones'' as target attributes.
We chose gender as the sensitive attribute as it a common sensitive attribute in the fairness literature.
For the target attributes, we chose attributes that are harder to learn than gender and which do not correlate too strongly with gender in the dataset
(``wearing lipstick'' for example being an attribute too closely correlated with gender).
% The sampling and evaluation procedure is identical to that conducted for the UCI Adult dataset.
% We evaluate the performance of all models for mixing factors ($\eta$) of value $\{0, 0.1, ..., 1\}$. 
The model is trained on the representative set (normal subset of CelebA)
and is then used to encode the artificially biased training set and the test set.
The results for the most strongly biased training set ($\eta=0$) can be found in fig.~\ref{fig:celeba-targets}.
Our method outperforms the baselines in accuracy and fairness.

We also assess performance for different mixing factors ($\eta$) which correspond to varying degrees of bias in the training set
(see fig.~\ref{fig:celeba-multiplot}).
This is to verify that the model does not \emph{harm} performance when there is not much bias in the training set.
For these experiments, the model is trained once on the representative set and is then used to encode different training sets.
The results show that for the intermediate values of $\eta$, our model incurs a small penalty in terms of accuracy,
but at the same time makes the results \emph{fairer} (corresponding to an accuracy-fairness trade-off). Qualitative results can be found in fig.~\ref{fig:celeba_cflow} (images from cVAE can be found in section~\ref{sec:qual-results-celeba}).

@@

\paragraph{Results for the UCI Adult dataset.}
The UCI Adult dataset consists of census data and is commonly used to evaluate models focused on algorithmic fairness.
Following convention, we designate ``gender'' as the sensitive attribute $s$ and whether an individual's salary is \$50,000 or greater as $y$.
We show the performance of our approach in comparison to baseline approaches in fig. \ref{fig:adult-chart}.
We evaluate the performance of all models for mixing factors ($\eta$) $0$ and $1$. 
Results shown in fig. \ref{fig:adult-chart} show that
%while our model fails to surpass the baseline models in terms of accuracy for the balanced case (and those close to it),
we match or exceed the baseline.
%as $\eta$ moves the dataset towards a more imbalanced setting.
In terms of fairness metrics, our approach generally outperforms the baseline models for both of $\eta$.
Detailed results can be found in the Appendix~\ref{sec:additional-results}.
